---
title: "Europe and Asia"
author: "Gabriela Lozano"
date: "6/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Covid Cases in Europe and Asia

This document includes code for plots and data management of different values and the process that went to it.
It includes Europe and Asia data in relation to weather and gdp.
##Import Libraries

```{r}
library(ggplot2)
library(ggpubr)
library(dplyr)
library(weathermetrics)
```

## Read Data and merge them together

```{r}
#Read in data
covid_cases = read.csv("https://covid.ourworldindata.org/data/owid-covid-data.csv") # Read-in data
weather= read.csv("Weather_Data_Cleaned.csv")


#Change the name of the column
names(weather)[names(weather) == "CTRY"] <- "location"
weather = merge(weather, covid_cases, by="location")

#Add a column with the month
weather$month = gsub("2020-", "", weather$date) # Remove year and hyphen
weather$month = gsub("-", "", weather$month) # remove extra hyphen
weather$month = substr(weather$month, 1, nchar(weather$month) - 2) # remove day of month


#Change weather to C instead of F
weather$MAR = fahrenheit.to.celsius(weather$MAR)
weather$APR = fahrenheit.to.celsius(weather$APR)
weather$MAY = fahrenheit.to.celsius(weather$MAY)

```
After we do that we take the values from Europe.
## Getting amount of cases per month from Europe data
```{r}
#Make dataframe
europedf = weather %>% filter(continent == "Europe")

# Add Frequency per months of Europe
#March
europemar = europedf %>% filter(month == "03")
freqdf = data.frame(tapply(europemar$new_cases, europemar$location, FUN=sum) )
freqdf <- tibble::rownames_to_column(freqdf, "VALUE")
names(freqdf)[1] <-"location"
names(freqdf)[2] <- "frequency"

freqddf =data.frame(tapply(europemar$new_deaths, europemar$location, FUN=sum) )
freqddf = tibble::rownames_to_column(freqddf, "VALUE")
names(freqddf)[1] <-"location"
names(freqddf)[2] <- "deathfreq"
Efreqdf = merge(freqdf, freqddf, by="location")
europemar = merge(europemar, Efreqdf, by="location")

#April
europeapr = europedf %>% filter(month == "04")
freqdf = data.frame(tapply(europeapr$new_cases, europeapr$location, FUN=sum) )
freqdf <- tibble::rownames_to_column(freqdf, "VALUE")
names(freqdf)[1] <-"location"
names(freqdf)[2] <- "frequency"

freqddf =data.frame(tapply(europeapr$new_deaths, europeapr$location, FUN=sum) )
freqddf = tibble::rownames_to_column(freqddf, "VALUE")
names(freqddf)[1] <-"location"
names(freqddf)[2] <- "deathfreq"
Efreqdf = merge(freqdf, freqddf, by="location")
europeapr = merge(europeapr, Efreqdf, by="location")

#May
europemay = europedf %>% filter(month == "05")
freqdf = data.frame(tapply(europemay$new_cases, europemay$location, FUN=sum) )
freqdf <- tibble::rownames_to_column(freqdf, "VALUE")
names(freqdf)[1] <-"location"
names(freqdf)[2] <- "frequency"

freqddf =data.frame(tapply(europemay$new_deaths, europemay$location, FUN=sum) )
freqddf = tibble::rownames_to_column(freqddf, "VALUE")
names(freqddf)[1] <-"location"
names(freqddf)[2] <- "deathfreq"
Efreqdf = merge(freqdf, freqddf, by="location")
europemay = merge(europemay, Efreqdf, by="location")
```
Then we can get the frequencies for each month and afterwards we can plot these values. We include both Temperature and GDP in these graphs.
##March in Europe
```{r, echo=FALSE}
#Getting rates for cases and deaths and added the log
MarMaxE = europemar[europemar$date == max(europemar$date),]
MarMaxE$freqpop = MarMaxE$frequency/MarMaxE$population
MarMaxE$freqdead = MarMaxE$deathfreq/MarMaxE$population
MarMaxE$freqpoplog = log(MarMaxE$freqpop)
MarMaxE$freqdeadlog = log(MarMaxE$freqdead)


#Temperature
ggscatter(MarMaxE, x = 'MAR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in European Countries",
          label="location", repel=TRUE)

ggscatter(MarMaxE, x = 'MAR', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Deaths in March",
          title="Rate of Deaths in March in European Countries",
          label="location", repel=TRUE)
#GDP
ggscatter(MarMaxE, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in European Countries",
          label="location", repel=TRUE)

ggscatter(MarMaxE, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths in March",
          title="Rate of Deaths in March in European Countries",
          label="location", repel=TRUE)
```
Now we do something similar for both April and May

##April in Europe
```{r}
AprMaxE = europeapr[europeapr$date == max(europeapr$date),]
AprMaxE$freqpop = AprMaxE$frequency/AprMaxE$population
AprMaxE$freqdead = AprMaxE$deathfreq/AprMaxE$population
AprMaxE$freqpoplog = log(AprMaxE$freqpop)
AprMaxE$freqdeadlog = log(AprMaxE$freqdead)

#Temperature
ggscatter(AprMaxE, x = 'APR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in European Countries",
          label="location", repel=TRUE)

ggscatter(AprMaxE, x = 'APR', y ='freqdeadlog',
          xlim =c(-5,25),
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Deaths in April",
          title="Rate of Deaths in April in European Countries",
          label="location", repel=TRUE)

#GDP
ggscatter(AprMaxE, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in European Countries",
          label="location", repel=TRUE)

ggscatter(AprMaxE, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths in April",
          title="Rate of Deaths in April in European Countries",
          label="location", repel=TRUE)
```
And now with May.

##May in Europe
```{r}
#Graphs for May
MayMaxE = europemay[europemay$date == max(europemay$date),]
MayMaxE$freqpop = MayMaxE$frequency/MayMaxE$population
MayMaxE$freqdead = MayMaxE$deathfreq/MayMaxE$population
MayMaxE$freqpoplog = log(MayMaxE$freqpop)
MayMaxE$freqdeadlog = log(MayMaxE$freqdead)

#Temperature
ggscatter(MayMaxE, x = 'MAY', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in European Countries",
          label="location", repel=TRUE)

ggscatter(MayMaxE, x = 'MAY', y ='freqdeadlog',
                    xlim =c(-5,25),
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Deaths in May",
          title="Rate of Deaths in May in European Countries",
          label="location", repel=TRUE, xaxis=c(-5,25))

#GDP
ggscatter(MayMaxE, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in European Countries",
          label="location", repel=TRUE)

ggscatter(MayMaxE, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths in May",
          title="Rate of Deaths in May in European Countries",
          label="location", repel=TRUE)

```
And now we do a similar procedure with the data for Asian Countries

First we get the amount of cases for each month in Asian Countries
##Asia
```{r}

#Gather data from Asia
asiadf = weather %>% filter(continent == "Asia")


#March
asiamar = asiadf %>% filter(month == "03")
freqdf = data.frame(tapply(asiamar$new_cases, asiamar$location, FUN=sum) )
freqdf <- tibble::rownames_to_column(freqdf, "VALUE")
names(freqdf)[1] <-"location"
names(freqdf)[2] <- "frequency"

freqddf =data.frame(tapply(asiamar$new_deaths, asiamar$location, FUN=sum) )
freqddf = tibble::rownames_to_column(freqddf, "VALUE")
names(freqddf)[1] <-"location"
names(freqddf)[2] <- "deathfreq"
Afreqdf = merge(freqdf, freqddf, by="location")
asiamar = merge(asiamar, Afreqdf, by="location")

#April
asiaapr = asiadf %>% filter(month == "04")
freqdf = data.frame(tapply(asiaapr$new_cases, asiaapr$location, FUN=sum) )
freqdf <- tibble::rownames_to_column(freqdf, "VALUE")
names(freqdf)[1] <-"location"
names(freqdf)[2] <- "frequency"

freqddf =data.frame(tapply(asiaapr$new_deaths, asiaapr$location, FUN=sum) )
freqddf = tibble::rownames_to_column(freqddf, "VALUE")
names(freqddf)[1] <-"location"
names(freqddf)[2] <- "deathfreq"
Afreqdf = merge(freqdf, freqddf, by="location")
asiaapr = merge(asiaapr, Afreqdf, by="location")

#May
asiamay = asiadf %>% filter(month == "05")
freqdf = data.frame(tapply(asiamay$new_cases, asiamay$location, FUN=sum) )
freqdf <- tibble::rownames_to_column(freqdf, "VALUE")
names(freqdf)[1] <-"location"
names(freqdf)[2] <- "frequency"

freqddf =data.frame(tapply(asiamay$new_deaths, asiamay$location, FUN=sum) )
freqddf = tibble::rownames_to_column(freqddf, "VALUE")
names(freqddf)[1] <-"location"
names(freqddf)[2] <- "deathfreq"
Afreqdf = merge(freqdf, freqddf, by="location")
asiamay = merge(asiamay, Afreqdf, by="location")
```
Then similarly to the previous part, we start graphing.
##March in Asia
```{r}
MarMaxA = asiamar[asiamar$date == max(asiamar$date),]
MarMaxA$freqpop = MarMaxA$frequency/MarMaxA$population
MarMaxA$freqdead = MarMaxA$deathfreq/MarMaxA$population
MarMaxA$freqpoplog = log(MarMaxA$freqpop)
MarMaxA$freqdeadlog = log(MarMaxA$freqdead)

#Temperature
ggscatter(MarMaxA, x = 'MAR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in Asian Countries",
          label="location", repel=TRUE)

ggscatter(MarMaxA, x = 'MAR', y ='freqdeadlog',
          xlim =c(5,32),
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Deaths in March",
          title="Rate of Deaths in March in Asian Countries",
          label="location", repel=TRUE)
#GDP
ggscatter(MarMaxA, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in Asian Countries",
          label="location", repel=TRUE)

ggscatter(MarMaxA, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths in March",
          title="Rate of Deaths in March in Asian Countries",
          label="location", repel=TRUE)
```
Then we do the one for Asia.
##April in Asia
```{r}
#Graphs for April
AprMaxA = asiaapr[asiaapr$date == max(asiaapr$date),]
AprMaxA$freqpop = AprMaxA$frequency/AprMaxA$population
AprMaxA$freqdead = AprMaxA$deathfreq/AprMaxA$population
AprMaxA$freqpoplog = log(AprMaxA$freqpop)
AprMaxA$freqdeadlog = log(AprMaxA$freqdead)

#Temperature
ggscatter(AprMaxA, x = 'APR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in Asian Countries",
          label="location", repel=TRUE)

ggscatter(AprMaxA, x = 'APR', y ='freqdeadlog',
                                        xlim =c(5,32),
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Deaths in April",
          title="Rate of Deaths in April in Asian Countries",
          label="location", repel=TRUE)
#GDP
ggscatter(AprMaxA, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in Asian Countries",
          label="location", repel=TRUE)

ggscatter(AprMaxA, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths in April",
          title="Rate of Deaths in April in Asian Countries",
          label="location", repel=TRUE)
```
And finally we do it for May
##May in Asia
```{r}
#Graphs for May
MayMaxA = asiamay[asiamay$date == max(asiamay$date),]
MayMaxA$freqpop = MayMaxA$frequency/MayMaxA$population
MayMaxA$freqdead = MayMaxA$deathfreq/MayMaxA$population
MayMaxA$freqpoplog = log(MayMaxA$freqpop)
MayMaxA$freqdeadlog = log(MayMaxA$freqdead)

#Temperature
ggscatter(MayMaxA, x = 'MAY', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in Asian Countries",
          label="location", repel=TRUE)

ggscatter(MayMaxA, x = 'MAY', y ='freqdeadlog',
                              xlim =c(5,32),
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Deaths in May",
          title="Rate of Deaths in May in Asian Countries",
          label="location", repel=TRUE)

#GDP
ggscatter(MayMaxA, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in Asian Countries",
          label="location", repel=TRUE)

ggscatter(MayMaxA, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths in May",
          title="Rate of Deaths in May in Asian Countries",
          label="location", repel=TRUE)
```
##Testing for outliers in Europe data
```{r}

#Cooks Distance on freq pop log
rownames(MarMaxE) <- 1:nrow(MarMaxE)
#Building linear model
frqmarlm = lm(freqpoplog~MAR, data=MarMaxE)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MarMaxE)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MarMaxE[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in Cold Countries",
          label="location", repel=TRUE) 

#Freq dead log
frqmarlm = lm(MarMaxE$freqdeadlog[which(MarMaxE$freqdeadlog != -Inf)] ~ MarMaxE$MAR[which(MarMaxE$freqdeadlog != -Inf)], data=MarMaxE)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MarMaxE)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MarMaxE[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in Cold Countries",
          label="location", repel=TRUE) 



```
##April outliers
```{r}
#Cooks Distance on freq pop log
rownames(AprMaxE) <- 1:nrow(AprMaxE)
#Building linear model
frqmarlm = lm(freqpoplog~APR, data=AprMaxE)
cooksd = cooks.distance(frqmarlm)

n <- nrow(AprMaxE)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AprMaxE[-influential_obs, ]
ggscatter(othergmarchdc, x = 'APR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in Cold Countries",
          label="location", repel=TRUE) 

#Freq dead log
frqmarlm = lm(AprMaxE$freqdeadlog[which(AprMaxE$freqdeadlog != -Inf)] ~ AprMaxE$APR[which(AprMaxE$freqdeadlog != -Inf)], data=AprMaxE)
cooksd = cooks.distance(frqmarlm)

n <- nrow(AprMaxE)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AprMaxE[-influential_obs, ]
ggscatter(othergmarchdc, x = 'APR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in Cold Countries",
          label="location", repel=TRUE) 
```
## May Outliers
```{r}
#Cooks Distance on freq pop log
rownames(MayMaxE) <- 1:nrow(MayMaxE)
#Building linear model
frqmarlm = lm(MayMaxE$freqpoplog[which(MayMaxE$freqpoplog != -Inf)] ~ MayMaxE$MAY[which(MayMaxE$freqpoplog != -Inf)], data=MayMaxE)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MayMaxE)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MayMaxE[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAY', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in Cold Countries",
          label="location", repel=TRUE) 

#Freq dead log
frqmarlm = lm(MayMaxE$freqdeadlog[which(MayMaxE$freqdeadlog != -Inf)] ~ MayMaxE$MAY[which(MayMaxE$freqdeadlog != -Inf)], data=MayMaxE)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MayMaxE)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MayMaxE[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAY', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in Cold Countries",
          label="location", repel=TRUE) 

```
And now for Asia
#Asia outliers
```{r}

#Cooks Distance on freq pop log
rownames(MarMaxA) <- 1:nrow(MarMaxA)
#Building linear model
frqmarlm = lm(freqpoplog~MAR, data=MarMaxA)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MarMaxA)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MarMaxA[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in Cold Countries",
          label="location", repel=TRUE) 

#Freq dead log
frqmarlm = lm(MarMaxA$freqdeadlog[which(MarMaxA$freqdeadlog != -Inf)] ~ MarMaxA$MAR[which(MarMaxA$freqdeadlog != -Inf)], data=MarMaxA)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MarMaxA)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MarMaxA[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in March",
          title="Rate of Cases in March in Cold Countries",
          label="location", repel=TRUE) 



```

April:
##April outliers
```{r}
#Cooks Distance on freq pop log
rownames(AprMaxA) <- 1:nrow(AprMaxA)
#Building linear model
frqmarlm = lm(freqpoplog~APR, data=AprMaxA)
cooksd = cooks.distance(frqmarlm)

n <- nrow(AprMaxA)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AprMaxA[-influential_obs, ]
ggscatter(othergmarchdc, x = 'APR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in Cold Countries",
          label="location", repel=TRUE) 

#Freq dead log
frqmarlm = lm(AprMaxA$freqdeadlog[which(AprMaxA$freqdeadlog != -Inf)] ~ AprMaxA$APR[which(AprMaxA$freqdeadlog != -Inf)], data=AprMaxA)
cooksd = cooks.distance(frqmarlm)

n <- nrow(AprMaxA)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AprMaxA[-influential_obs, ]
ggscatter(othergmarchdc, x = 'APR', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in April",
          title="Rate of Cases in April in Cold Countries",
          label="location", repel=TRUE) 
```

May:
##April outliers
```{r}
#Cooks Distance on freq pop log
rownames(MayMaxA) <- 1:nrow(MayMaxA)
#Building linear model
frqmarlm = lm(MayMaxA$freqpoplog[which(MayMaxA$freqpoplog != -Inf)] ~ MayMaxA$MAY[which(MayMaxA$freqpoplog != -Inf)], data=MayMaxA)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MayMaxA)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MayMaxA[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAY', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in Cold Countries",
          label="location", repel=TRUE) 

#Freq dead log
frqmarlm = lm(MayMaxA$freqdeadlog[which(MayMaxA$freqdeadlog != -Inf)] ~ MayMaxA$MAY[which(MayMaxA$freqdeadlog != -Inf)], data=MayMaxA)
cooksd = cooks.distance(frqmarlm)

n <- nrow(MayMaxA)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- MayMaxA[-influential_obs, ]
ggscatter(othergmarchdc, x = 'MAY', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Temperature", ylab = "Rate of Cases in May",
          title="Rate of Cases in May in Cold Countries",
          label="location", repel=TRUE) 


```

##European data outliers for gdp
```{r}
EuropeLD = europedf[europedf$date == max(europedf$date),]
EuropeLD$freqpop = EuropeLD$total_cases/EuropeLD$population
EuropeLD$freqdead = EuropeLD$total_deaths/EuropeLD$population
EuropeLD$freqpoplog = log(EuropeLD$freqpop)
EuropeLD$freqdeadlog = log(EuropeLD$freqdead)

#Cooks Distance on freq pop log
rownames(EuropeLD) <- 1:nrow(EuropeLD)
#Building linear model
frqmarlm = lm(freqpoplog~gdp_per_capita, data=EuropeLD)
cooksd = cooks.distance(frqmarlm)

n <- nrow(EuropeLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- EuropeLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(EuropeLD, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 


#Building linear model with death
frqmarlm = lm(freqdeadlog~gdp_per_capita, data=EuropeLD)
cooksd = cooks.distance(frqmarlm)

n <- nrow(EuropeLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- EuropeLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(EuropeLD, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 

```
##Asian data outliers for gdp
```{r}
AsiaLD = asiadf[asiadf$date == max(asiadf$date),]
AsiaLD$freqpop = AsiaLD$total_cases/AsiaLD$population
AsiaLD$freqdead = AsiaLD$total_deaths/AsiaLD$population
AsiaLD$freqpoplog = log(AsiaLD$freqpop)
AsiaLD$freqdeadlog = log(AsiaLD$freqdead)

#Cooks Distance on freq pop log
rownames(AsiaLD) <- 1:nrow(AsiaLD)
#Building linear model
frqmarlm = lm(freqpoplog~gdp_per_capita, data=AsiaLD)
cooksd = cooks.distance(frqmarlm)

n <- nrow(AsiaLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AsiaLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(AsiaLD, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 


#Building linear model with death
frqmarlm = lm(AsiaLD$freqdeadlog[which(AsiaLD$freqdeadlog != -Inf)] ~ AsiaLD$gdp_per_capita[which(AsiaLD$freqdeadlog != -Inf)])
cooksd = cooks.distance(frqmarlm)

n <- nrow(AsiaLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AsiaLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(AsiaLD, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 

```
Now, I want to graph the GDP plots again but excluding countries with a low death rate
```{r}
EuropeLD = europedf[europedf$date == max(europedf$date),]
EuropeLD = EuropeLD[EuropeLD$total_deaths > quantile(EuropeLD$total_deaths, .25, names = FALSE),]
EuropeLD$freqpop = EuropeLD$total_cases/EuropeLD$population
EuropeLD$freqdead = EuropeLD$total_deaths/EuropeLD$population
EuropeLD$freqpoplog = log(EuropeLD$freqpop)
EuropeLD$freqdeadlog = log(EuropeLD$freqdead)

#Cooks Distance on freq pop log
rownames(EuropeLD) <- 1:nrow(EuropeLD)
#Building linear model
frqmarlm = lm(freqpoplog~gdp_per_capita, data=EuropeLD)
cooksd = cooks.distance(frqmarlm)

n <- nrow(EuropeLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- EuropeLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(EuropeLD, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 


#Building linear model with death
frqmarlm = lm(freqdeadlog~gdp_per_capita, data=EuropeLD)
cooksd = cooks.distance(frqmarlm)

n <- nrow(EuropeLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- EuropeLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(EuropeLD, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 

```
And now for Asia
```{r}
AsiaLD = asiadf[asiadf$date == max(asiadf$date),]
AsiaLD = AsiaLD[AsiaLD$total_deaths > quantile(AsiaLD$total_deaths, .25, names = FALSE),]
AsiaLD$freqpop = AsiaLD$total_cases/AsiaLD$population
AsiaLD$freqdead = AsiaLD$total_deaths/AsiaLD$population
AsiaLD$freqpoplog = log(AsiaLD$freqpop)
AsiaLD$freqdeadlog = log(AsiaLD$freqdead)

#Cooks Distance on freq pop log
rownames(AsiaLD) <- 1:nrow(AsiaLD)
#Building linear model
frqmarlm = lm(freqpoplog~gdp_per_capita, data=AsiaLD)
cooksd = cooks.distance(frqmarlm)

n <- nrow(AsiaLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AsiaLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(AsiaLD, x = 'gdp_per_capita', y ='freqpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Cases with respect to GDP",
          label="location", repel=TRUE) 


#Building linear model with death
frqmarlm = lm(AsiaLD$freqdeadlog[which(AsiaLD$freqdeadlog != -Inf)] ~ AsiaLD$gdp_per_capita[which(AsiaLD$freqdeadlog != -Inf)])
cooksd = cooks.distance(frqmarlm)

n <- nrow(AsiaLD)
plot(cooksd, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")
#Plotting
plot(cooks.distance(frqmarlm))
influential_obs <- as.numeric(names(cooksd)[(cooksd > (4/n))])
othergmarchdc <- AsiaLD[-influential_obs, ]
ggscatter(othergmarchdc, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W/O: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 
ggscatter(AsiaLD, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Cases",
          title="W: Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 

```
##Excess deaths
```{r}
excessdeaths = read.csv("excess-deaths.csv")
bydates = excessdeaths %>%group_by(country) %>% summarize(date=max(date))
excessdeaths = merge(bydates, excessdeaths, by=c("date", "country"))
names(excessdeaths)[names(excessdeaths) == "country"] <- "location"
excessdeaths$location[5] <- "United States"
#lastday = weather[weather$date == max(weather$date),]
lastday = weather %>%group_by(location) %>% summarize(date=max(date))
lastday = merge(lastday, weather, by=c("location", "date"))
excessdeaths = excessdeaths[c(2,3)]
extravalues = merge(excessdeaths, lastday, by="location")

extravalues$freqpop = extravalues$total_cases/extravalues$population
extravalues$freqdead = extravalues$total_deaths/extravalues$population
extravalues$freqpoplog = log(extravalues$freqpop)
extravalues$freqdeadlog = log(extravalues$freqdead)
extravalues$excessdeath = extravalues$total_deaths + extravalues$fitted
extravalues$excessdeathpop = extravalues$excessdeath/extravalues$population
extravalues$excessdeathpoplog = log(extravalues$excessdeathpop)

ggscatter(extravalues, x = 'gdp_per_capita', y ='excessdeathpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths",
          title="Rate of Deaths with Excess Deaths with respect to GDP",
          label="location", repel=TRUE) 

ggscatter(extravalues, x = 'gdp_per_capita', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths",
          title="Rate of Deaths with respect to GDP",
          label="location", repel=TRUE) 


ggscatter(extravalues, x = 'MAR', y ='excessdeathpoplog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths",
          title="W: Rate of Deaths with respect to Temp in March",
          label="location", repel=TRUE) 

ggscatter(extravalues, x = 'MAR', y ='freqdeadlog',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "GDP", ylab = "Rate of Deaths",
          title="W: Rate of Deaths with respect to Temp in March",
          label="location", repel=TRUE) 

ggplot(extravalues, aes(x=gdp_per_capita)) + 
  geom_point(aes(y = excessdeathpoplog), color = "darkred") + 
  geom_point(aes(y = freqdeadlog), color="steelblue", linetype="twodash")+
  ggtitle("Excess Deaths vs Observed Deaths in relation to GDP")+
  xlab("GDP")+
  ylab("Rate of Deaths")

```
